Selective enhancement of an exploited species undermines community stability

### 2021-12-01 rmd/manuscript.Rmd
edit: manuscript

EMPIRICAL ANALYSIS

>>>>

## Empirical evidence

To demonstrate the relevance of our general theory to natural systems, we assessed the potential impacts of selective enhancement of masu salmon on long-term stability of stream fish communities. Masu salmon represents one of the most valuable freshwater resources in Hokkaido Island, Japan, and XX leads extensive hatchery programs across the island. In protected watersheds where any form of exploitation is prohibited (including recreational angling), long-term monitoring has been conducted over the past two decades along with official records of the number of released fish. Hence, this dataset provides an excellent opportunity to evaluate how the selective enhancement influences long-term stability of stream fish communities. In this study, we assembled long-term data of stream fish communities at XX sites within XX protected watersheds (see Methods for selection criterion).

## Implications
